\begin{thebibliography}{99}
\setlength{\bibsep}{0pt plus 0.3ex}
%\addcontentsline{toc}{chapter}{Bibliografia}
\bibitem{Heim98} Heim M.: \emph{Virtual realism}. Oxford University Press, New York, 1998.

\bibitem{Fuchs92} Fuchs H., Bishop G. et al.: \emph{Research Directions in Virtual Environments}. NFS
Invitational Workshop, Univ. North Carolina, 1992.

\bibitem{Cruz93} Cruz-Neira C.: \emph{Virtual Reality Overview}, SIGGRAPH’93 Course, 23, 1.1-1.18, 1993.

\bibitem{Sherman03} Sherman W., Craig W.: \emph{Understanding Virtual Reality. Interface, Application and Design}. Morgan Kaufmann Publishers, San Francisco, 2003.

\bibitem{Milgram94} Milgram P., Takemura H., Ustumi A., Kishino F: \emph{Augmented Reality: A class of displays on the reality-virtuality continuum}. SPIE proc. Telemanipulator and Telepresence Technologies, 2351: 282-292, 1994.

\bibitem{Olszewski15} Olszewski P.: \emph{Historia wirtualnej rzeczywistości}, 2015. Retrieved January 20, 2016, from [\url{http://www.komputerswiat.pl/centrum-wiedzy-konsumenta/gaming/wszystko-o-wirtualnej-rzeczywistosci/historia-wirtualnej-rzeczywistosci.aspx}].

\bibitem{Mandal13} Mandal S.: \emph{Brief Introduction of Virtual Reality \& its Challenges}. International Journal of Scientific \& Engineering Research, 4, 4: 304-309, 2013.

\bibitem{Lange10} Lange B.S. et al.: \emph{The Potential of Virtual Reality and Gaming to Assist Successful Aging with Disability}. Physical medicine and rehabilitation clinics of North America, 21.2: 339-356, 2010.

\bibitem{Brooks99} Brooks Jr. F.P.: \emph{What’s Real About Virtual Reality?} IEEE Computer Graphics and Applications, 19, 6: 16-27, 1999.

\bibitem{Mazuryk96} Mazuryk T., Gervautz M.: \emph{Virtual Reality History, Applications, Technology and Future}. Institute of Computer Graphics, Vienna University of Technology, 1996. Retrieved January 20, 2016, from [\url{https://www.cg.tuwien.ac.at/research/publications/1996/mazuryk-1996-VRH/TR-186-2-96-06Paper.pdf}].

\bibitem{Wikibook15} Wikibooks contributors: \emph{Cg Programming/Unity/Projection for Virtual Reality}, Wikibooks, The Free Textbook Project, 2015. Retrieved January 25, 2016, from [\url{https://en.wikibooks.org/w/index.php?title=Cg_Programming/Unity/Projection_for_Virtual_Reality&oldid=2988608}].

\bibitem{Oscillada15} Oscillada J.M.: \emph{Comparison Chart of FOV (Field of View) of VR Headsets}, 2015. Retrieved January 20, 2016, from [\url{http://www.virtualrealitytimes.com/2015/05/24/chart-fov-field-of-view-vr-headsets/}].

\bibitem{Lacrama07} Lacrama, Dan L.; Fera D.: \emph{Virtual Reality}. Ann. Univ. Tibiscus, Computer Science Series V, 1: 137-144, 2007.

\bibitem{Parisi15} Parisi T.: \emph{Learning Virtual Reality}. O'Reily Media, Sebastopol, 2015.

\bibitem{Gobbetti99} Gobbetti E., Scateni R.: \emph{Virtual reality: Past, present, and future}. Virtual Environments in Clinical Psychology and Neuroscience: Methods and Techniques in Advanced Patient-Therapist Interaction, 3-20, IOS, Amsterdam, 2015.

\bibitem{Oculus16} \emph{Oculus Rift Documentation}, 2016. Retrieved January 27, 2016, from [\url{https://developer.oculus.com/documentation/}].

\bibitem{Feelreal16} \emph{FeelReal official website}, 2016. Retrieved January 27, 2016, from [\url{http://feelreal.com/smells}].

\bibitem{Marco15} Marco J.: \emph{List of Haptic Controllers under Development for Virtual Reality}, 2015. Retrieved January 27, 2016, from [\url{http://www.virtualrealitytimes.com/2015/03/13/list-of-haptic-controllers-virtual-reality/}].

\bibitem{Roadtovr14} \emph{Overview of Positional Tracking Technologies for Virtual Reality}, 2014. Retrieved February 06, 2016, from [\url{http://www.roadtovr.com/overview-of-positional-tracking-technologies-virtual-reality/}].

\bibitem{Weichert13} Weichert F., Bachamn D., Rudak B., Fisseler D.: \emph{Analysis of the Accuracy and Robustness of the Leap Motion Controller}. Sensors (Basel, Switzerland), 13(5): 6380-6393, 2013.

\bibitem{Leap16} \emph{Leap Motion Documentation}, 2016. Retrieved May 06, 2016, from [\url{https://developer.leapmotion.com/documentation/}].

\bibitem{Singal15} Singal N.: \emph{Magic Realism}, 2014. Business Today, November 8, 205-208, 2015.

\bibitem{Goodsell04} Goodsell D.S.: \emph{Bionanotechnology : lessons from nature}. Wiley-Liss, Inc., Hoboken, New Jersey, 2004. 

\bibitem{Gruca10} Gruca A.: \emph{Bioinformatyczne bazy danych}. Wydawnictwo PJWSTK, Warszawa 2010. 

\bibitem{Anderson99} Anderson A., Weng Z.: \emph{VRDD: Applying virtual reality visualization to protein docking and design}. Journal of Molecular Graphics and Modelling, 17: 180-186, 1999.

\bibitem{Schulze11} Schulze J.P. et al.: \emph{Advanced applications of virtual reality}. Advances in Computers, 82: 217-260. Academic Press, Burlington 2011.

\bibitem{Herisson05} Hérisson J. et al.: \emph{3D visualization and virtual exploration of genomic sequences}. Data Science Journal, 4: 82-91, 2005.

\bibitem{Hamdi08} Hamdi M. et al.: \emph{Prototyping bio-nanorobots using molecular dynamics simulation and virtual reality}. Microelectronics Journal, 39: 190–201, 2008.

\bibitem{Norrby15} Norrby M. et al.: \emph{Molecular Rift: Virtual Reality for Drug Designers}. Journal of Chemical Information and Modeling, 55: 2475-2484, 2015.

\bibitem{Koltun65} Koltun W.L.: \emph{Space filling atomic units and connectors for molecular models}. U. S. Patent 3170246, 1965.

\bibitem{Rasmol16} \emph{Rasmol v2.6 Manual}, 2016. Retrieved May 06, 2016, from [\url{http://life.nthu.edu.tw/~fmhsu/rasframe/TOC.HTM}].


\end{thebibliography}